---
title: "Medium Test Analysis"
output: github_document
---

## Introduction

This document demonstrates the analysis of XML data using R, focusing on extracting information about movies from an XML string. The analysis leverages the `XML` library in R to parse and manipulate XML data.

## Setting Up the Environment

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE)
```

## XML Data

The XML string contains information about two movies, including their titles, directors, release years, and genres. The structure of the XML string is hierarchical, with each movie enclosed within `<movie>` tags.

```{r xml_string, echo=TRUE} 
library(XML)
xml_content <- c(
    '<?xml version="1.0" encoding="UTF-8"?>',
    "<movies>",
    '<movie mins="126" lang="eng">',
    "<title>Good Will Hunting</title>",
    "<director>",
    "<first_name>Gus</first_name>",
    "<last_name>Van Sant</last_name>",
    "</director>",
    "<year>1998</year>",
    "<genre>drama</genre>",
    "</movie>",
    '<movie mins="106" lang="spa">',
    "<title>Y tu mama tambien</title>",
    "<director>",
    "<first_name>Alfonso</first_name>",
    "<last_name>Cuaron</last_name>",
    "</director>",
    "<year>2001</year>",
    "<genre>drama</genre>",
    "</movie>",
    "</movies>"
)
```

## Parsing XML Data

To analyze the XML data, we first need to parse it into an R object. The `xmlTreeParse` function from the `XML` library is used for this purpose. This function converts the XML string into an XML document object, which can then be manipulated using R.

```{r read_xml, echo=TRUE} 
xml_doc <- xmlTreeParse(paste(xml_content, collapse = ""), useInternalNodes = TRUE)
print(xml_doc)
```

## Extracting Movie Information

To extract information about the movies, we use the `xmlRoot` function to access the root node of the XML document. We then iterate over the child nodes of the root node, which represent the movies, and extract their information.

```{r extract_movie, echo=TRUE} 
movies_node <- xmlRoot(xml_doc)

cat("Root Node Name:", xmlName(movies_node), "\n")

root_attrs <- xmlAttrs(movies_node)

cat("Root Node Attributes:", "\n")

print(root_attrs)

movie_nodes <- xmlChildren(movies_node)
```

## Iterate through each Movie child node and display Information

```{r display_movie_info, echo=TRUE} 
for (i in seq_along(movie_nodes)) {
    movie_node <- movie_nodes[[i]]

    cat("Movie Node", i, "Name:", xmlName(movie_node), "\n")

    movie_attrs <- xmlAttrs(movie_node)

    cat("Movie Node", i, "Attributes:", "\n")

    print(movie_attrs)

    movie_children <- xmlChildren(movie_node)

    for (j in seq_along(movie_children)) {
        child_node <- movie_children[[j]]

        cat("Child Node", j, "Name:", xmlName(child_node), "\n")

        cat("Child Node", j, "Content:", xmlValue(child_node), "\n")

        child_attrs <- xmlAttrs(child_node)

        cat("Child Node", j, "Attributes:", "\n")
        print(child_attrs)
    }

    cat("\n")
}
```