---
title: "Medium Test Analysis"
output: pdf_document
---

## Introduction

The medium test aims to **replicate** the **analysis** conducted in Section 41.1.3 using functions from the **XML** package. This test focuses on transforming XML data into a **structured** **data frame** for further analysis and reporting. The XML package, being an older package, offers a straightforward way to convert XML data into data frames, which is particularly useful for handling nested XML structures.The XML document provided in the test is a nested structure, with each \<**node**\> element containing potentially **nested** \<**node**\> elements (and some containing attributes). The goal is to extract specific information from this XML document, such as the **text** values, **length**, **attributes**,**name**,**children** etc. of nested \<node\> elements under the root \<node\> element.

## Setting Up the Environment

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE)
```

### [Section 1: Loading Libraries and parsing XML Content]{.underline}

```{r message=FALSE}

library(XML)

xml_content <- c(
 '<?xml version="1.0" encoding="UTF-8"?>',
 '<movies>',
 '<movie mins="126" lang="eng">',
 '<title>Good Will Hunting</title>',
 '<director>',
 '<first_name>Gus</first_name>',
 '<last_name>Van Sant</last_name>',
 '</director>',
 '<year>1998</year>',
 '<genre>drama</genre>',
 '</movie>',
 '<movie mins="106" lang="spa">',
 '<title>Y tu mama tambien</title>',
 '<director>',
 '<first_name>Alfonso</first_name>',
 '<last_name>Cuaron</last_name>',
 '</director>',
 '<year>2001</year>',
 '<genre>drama</genre>',
 '</movie>',
 '</movies>'
)
```

**Explanation**

-   The **XML** library is loaded to handle XML data in R.

-   An XML content string representing a list of movies is defined, including details like **title**, **director**, **year**, and **genre**.

```{r message=FALSE}

doc <- xmlTreeParse(paste(xml_content, collapse = ''), useInternalNodes = TRUE)
doc
```

**Explanation**

-   The **xmlTreeParse** function from the XML package is used to parse the XML string into an XML document object.

-   The **paste** function with **collapse = ' '** is used to concatenate the XML string into a single string before parsing.

-   The **useInternalNodes** = **TRUE** argument specifies that the function should return an internal node, which is more efficient for extracting parts of the XML document[1](https://stackoverflow.com/questions/20684507/in-r-xml-package-what-is-the-difference-between-xmlparse-and-xmltreeparse).

-   The **parsed** XML document is stored in the variable xml_doc.\

### [Section 2: Navigation of XML Tree]{.underline}

#### [2.1 Access the root Node]{.underline}

```{r message=FALSE}

# Get the root node of the XML document
movies <- xmlRoot(doc)
movies

# Check if the XML document and the root node are identical
identical(doc, movies)
```

It turns out that `doc` and `movies` are not actually identical

**Explanation**

-   The **xmlRoot** function extracts the root node of the XML document, which is stored in movies.

-   The identical function checks if the **root** **node** is the same as the **original document**, demonstrating the structure of the XML document.

#### [2.2 Access the children of movies node]{.underline}

```{r message=FALSE}

# Access the child nodes of the root node
xmlChildren(movies)

# Access the first movie node
good_will <- xmlChildren(movies)[[1]]
good_will

# Access the second movie node
tu_mama <- xmlChildren(movies)[[2]]
tu_mama
```

**Explanation**

-   **xmlChildren(movies)** retrieves the child nodes of the node "movies".

-   **xmlChildren(movies)[[1]]** accesses the first movie node from the child nodes of "movies".

-   **xmlChildren(movies)[[2]]** accesses the second movie node from the child nodes of "movies".

### [Section 3: Inspecting first node]{.underline}

#### [3.1 Inspecting contents of the children of movies node]{.underline}

```{r message=FALSE}

# Access the children nodes of 'good_will'
xmlChildren(good_will)

# Access the children nodes of 'tu_mama'
xmlChildren(tu_mama)

# Get the name of the 'good_will' node
xmlName(good_will)

# Get the attributes of the 'good_will' node
xmlAttrs(good_will)

# Get the size (number of children) of the 'good_will' node
xmlSize(good_will)
```

**Explanation**

-   The **xmlName** function is used to get the name of the **good_will** node.

-   The **xmlAttrs** function is used to get the attributes of the root node.

-   The **xmlChildren** function lists all child nodes of the root node, which represent individual movies.

#### [3.2 Inspecting contents of good_will node]{.underline}

```{r message=FALSE}

# Iterate over each child node of 'good_will' and print their names
children_nodes <- xmlChildren(good_will)
for (node in children_nodes) {
  print(xmlName(node))
}

# Access the title node of 'good_will'
title1 <- xmlChildren(good_will)[["title"]]
title1

# Access the children nodes of 'title1'
xmlChildren(title1)

# Get the text content of 'title1'
xmlValue(title1)
```

**Explanation**

-   **xmlChildren(good_will)** retrieves the child nodes of the 'good_will' node.

-   **xmlChildren(good_will)[["title"]]** accesses the 'title' node within the 'good_will' node.

-   **xmlChildren(title1)** accesses the child nodes of the 'title1' node

-   **xmlValue(title1)** extracts the text content of the 'title1' node, representing the title of the movie.

### [Section 4: Inspecting director node]{.underline}

```{r message=FALSE}

# Access the director node of 'good_will' 
dir1 <- xmlChildren(good_will)[["director"]]
dir1

# Access the children nodes of 'dir1'
xmlChildren(dir1)

# Get the text content of 'dir1'
xmlValue(dir1)
```

**Explanation**

-   **xmlChildren(good_will)[["director"]]** accesses the 'director' node within the 'good_will' node.

-   **xmlChildren(dir1)** accesses the child nodes of the 'dir1' node.

-   **xmlValue(dir1)** extracts the text content of the 'dir1' node, representing the director's name.

The following **results** obtained from the code can be compared with the required section outlinedexample data set in [Section 41.1.3 of Computing with Data](https://www.gastonsanchez.com/intro2cwd/parsing.html#navigation-of-xml-html-tree)